### 2022-03-08 manuscript.tex
beginning of discussion section and updated images

\usepackage{framed}
\usepackage{changepage}
\usepackage{amsfonts}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

@@

\subsection{Representations}
\subsubsection{Parametric distributions}
A parametric distribution is a discrete or continuous probability distribution 
described by a known function $p(x) := p(x|\theta)$ -pmf in the discrete case or 
pdf in the continuous case. $\theta$ is a vector of known or unkown parameters 
contained in a parameter space.

@@

From a submitted forecast, a prediction may be found by Location, Target and 
Unit (or whatever other indication variables are used) and evaluated. We found
the \texttt{distr} \cite{camphausen2007distr}
useful for constructing a mixture distribution given
information like that from table \ref{tab:mstan}.

The function 
\texttt{UnivarMixingDistribution} takes as arguments a list of distributions
and a vector of weights for each distribution and a object pf a class called 
\texttt{AbscontDistribution} is returned. Functions for density, distribution
and quantile functions as well as for random sampling may then be used on the
mixture distribution object for evaluation. Using those functions and the 
created object, LogS and CRPS are easily calculable.

We wrote a function \texttt{MakeDist} which takes on a data frame with variables
Family, Param1, Param2, Param3 and Weight and returns a mixture distribution 
of component distributions specified in the rows.

@@

To construct an ensemble distribution from multiple mixture distributions, the 
\texttt{UnivarMixingDistribution} is again a useful tool. Two or more 
\texttt{AbscontDistribution} objects may be

Variables of R dataframe to b used in making mixture distribution 
\begin{center}
    \begin{tabular}{ | l | p{4cm} | p{7cm} |}
    \hline
    Argument & Summary & Options \\ \hline
    dist & A string specifying a distribution family.  & “Beta”, “Cauchy”, 
    “Lnorm”, “Logis”, “Unif”, “Lst” (location scale t distribution), 
    “Weibull”, “Fd”, “Norm”,  “Chisq”, 
    “Gammad”, “Exp”
	 “Binom”, “Dirac”, “Pois”, “Hyper”, “Nbinom”, “Geom” \\ \hline
    param1 & A real number specifying the first parameter value of the 
    distribution. & Beta: shape1; 
	Cauchy: location; 
	Lnorm: meanlog; 
	Logis: location; 
	Unif: min; 
	Lst: location; 
	Weibull: shape;
	Fd: df1;
	Norm: mean;
	Chisq: df;
	Gammad: scale;
	Exp: rate; 
	Binom: size;
	Dirac: location;
	Pois: lambda;
	Hyper: m;
	Nbinom: n;
	Geom: prob
     \\ \hline
    param2 & A real number specifying the second parameter value of the 
    distribution. & Beta: shape2; 
	Cauchy: scale; 
	Lnorm: slog; 
	Logis: scale; 
	Unif: Max; 
	Lst: scale; 
	Weibull: scale; 
	Fd: df2; 
	Norm: sd; 
	Chisq: ncp; 
	Gammad: shape; 
	Binom: prob; 
	Hyper: n; 
	Nbinom: p \\
    \hline
    param3 & A real number specifying the third parameter value of the 
    distribution. & Lst: df;
	Hyper: k \\
	\hline
	weight & A real number between 0 and 1 specifying the weight given to the 
	distribution in the overall mixture distribution. The sum of the weight 
	column should equal 1. & ...
	\\
	\hline
    \end{tabular}
\end{center}

\newpage
% \begin{adjustwidth}{-3cm}{-1cm}
\begin{center}
% \caption{MakeDist parameter options}
    \begin{tabular}{ l l  p{2cm}  p{2cm}  p{2cm}}
    \hline
    \textbf{Distribution} & \textbf{dist} & \textbf{param1} & \textbf{param2} & 
    \textbf{param3} \newline \\ \hline
    Beta & Beta & shape1 & shape2 &  \\ 
    Cauch & Cauchy & location & scale &  \\
    Log-normal & Lnorm & meanlog & slog &  \\
    Logistic & Logis & location & scale &  \\
    Uniform & Unif & min & max &  \\
    Location Scale T & Lst & location & scale & df \\
    Weibull & Weibull & shape & scale &  \\
    F & Fd & df1 & df2 &  \\
    Normal & Norm & mean & sd &  \\
    Chisqure & Chisq & df &  &  \\
    Gamma & Gammad & scale & shape &  \\
    Exponential & Exp & rate &  &  \\
    Binomial & Binom & size & prob &  \\
    Dirac & Dirac & location &  &  \\
    Poisson & Pois & lambda &  &  \\
    Hypergeometric & Hyper & m & n & k \\
    Negative binomial & Nbinom & n & p &  \\
    Geometric & Geom & prob &  &  \\ \hline
    \end{tabular}
\end{center}
% \end{adjustwidth}

>>>>

\usepackage{framed}
\usepackage{changepage}
\usepackage{amsfonts}
\usepackage{listings}
\usepackage[svgnames]{xcolor}

\lstset{language=R,
    basicstyle=\small\ttfamily,
    stringstyle=\color{DarkGreen},
    otherkeywords={0,1,2,3,4,5,6,7,8,9},
    morekeywords={TRUE,FALSE},
    deletekeywords={data,frame,length,as,character},
    keywordstyle=\color{blue},
    commentstyle=\color{DarkGreen},
}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

@@

\subsection{Representations}
\subsubsection{Parametric distributions}
\label{section:pardist}
A parametric distribution is a discrete or continuous probability distribution 
described by a known function $p(x) := p(x|\theta)$ -pmf in the discrete case or 
pdf in the continuous case. $\theta$ is a vector of known or unkown parameters 
contained in a parameter space.

@@

From a submitted forecast, a prediction may be found by Location, Target and 
Unit (or whatever other indication variables are used by collaborators) and 
evaluated. We found
the \texttt{distr} \cite{camphausen2007distr}
useful for constructing a mixture distribution given
information like that from table \ref{tab:mstan}.

The function 
\texttt{UnivarMixingDistribution} takes as arguments a list of distributions
and a vector of weights for each distribution and a object pf a class called 
\texttt{AbscontDistribution} is returned. The object is in essence a mixture
distribution of the form from (\ref{eq:dmd}). Functions for density, 
distribution
and quantile functions as well as for random sampling may then be used on the
mixture distribution object for evaluation. Using those functions and the 
created object, LogS and CRPS are easily calculable.

We wrote a function \texttt{MakeDist} (see appendix)
which takes on a data frame with variables
Family, Param1, Param2, Param3 and Weight and returns a mixture distribution 
of component distributions specified in the rows.

@@

To construct an ensemble distribution from multiple mixture distributions, the 
\texttt{UnivarMixingDistribution} is again a useful tool. The function takes 
two or more
\texttt{AbscontDistribution} or mixture distributions and a vector of weights 
corresponding to each mixture. A new \texttt{AbscontDistribution} object is 
returned as an ensemble of mixture distributions see (\ref{eq:bma}).

At the onset of a collaborative forecast before the various models can be scored
based on true observations, it may make sense to assign equal weight to each 
component distribution in an ensemble. As a project progresses however, 
assigning weights based on past performance may be desired. As mentioned in 
section \ref{section:pardist}, weights may be selected by maximizing the
likelihood of (\ref{eq:bma}) or by minimizing the CRPS. Another method of 
selecting weights is to use the posterior model probability.

If we have $T$ models ($M_t$) the posterior model probability of $M_t$ is 
defined as

\begin{equation}
\label{eq:pmp}
p(M_t|x) = \frac{p(x|M_t)p(M_t)}{p(x)}
         = \frac{p(x|M_t)p(M_t)}{\sum_{k=1}^T p(x|M_k)p(M_k)}
\end{equation}
where $p(\cdot |M_t) := p_m(\cdot)$ is the density function of the model and 
$p(M_j)$ is the prior probability assigned to the model. Where the prior
probabilities for each model are equal or $p(M_t) = 1/T$ for all $t$ 
(\ref{eq:pmp}) is reduced to

\begin{equation}
\label{eq:pmpeq}
p(M_t|x) =  \frac{p(x|M_t)}{\sum_{k=1}^Tp(x|M_k)}
\end{equation}

The posterior model probability $p(M_t|x^*)$ for an already observed event $x^*$
are then used as weights for a yet unrealized event being forecasted i.e.
$w_t := p(M_t|x^*)$ see (\ref{eq:bma}).

\subsection{Toy Example}

In the following example, a toy example is given of constructing two  
mixture distribution forecast prediction models from separate forecast 
submissions. The tools presented in this section are used in \texttt{R} code to
construct the distributions, build an ensemble consisting of both predictions 
and score the different models. In building the ensemble forecast, weights are
selected using the posterior model probability with equal prior probabilities
for both models (\ref{eq:pmpeq}).

Beginning with two forecast submissions of the form of table \ref{tab:mstan}, 
say we select from each a prediction of an event for the same location, target
and unit. The following two data frames \texttt{preddf1} and \texttt{preddf2}
are the resulting predictions.

\begin{table}[h!]
\label{tab:preddf1}
\centering
 \begin{tabular}{|c|c|c|c|c|}
 \hline
    family & param1 & param2 & param3 & weight
    \\ \hline
    Lnorm & 2 & 1 & NA & 0.3  \\
    Norm & 2.1 & 1 & NA & 0.7 \\
 \hline
 \end{tabular}
\end{table}

\begin{table}[h!]
\label{tab:preddf2}
\centering
 \begin{tabular}{|c|c|c|c|c|}
 \hline
    family & param1 & param2 & param3 & weight
    \\ \hline
    Norm & 1.5 & 1 & NA & 0.4  \\
    Norm & 4 & 2 & NA & 0.6 \\
 \hline
 \end{tabular}
\end{table}

The following code in \texttt{R} will construct mixture distributions, select
weights for an ensemble based on an observed realization, build the ensemble and 
score the forecasts using the
LogS and the CRPS.

\newpage
\begin{lstlisting}[language=R]

preddf1
#  family param1 param2 param3 weights
#1  Lnorm    2.0      1     NA     0.3
#2   Norm    2.1      1     NA     0.7

preddf2
#  family param1 param2 param3 weights
#1   Norm    1.5      1     NA     0.4
#2   Norm    4.0      2     NA     0.6

#make mixture distributions from prediction submissions
mdist1 <- MakeDist(preddf1)
mdist2 <- MakeDist(preddf2)

#make pdfs for mixture predictions
dmdist1 <- function(x) {distr::d(mdist1)(x)}
dmdist2 <- function(x) {distr::d(mdist2)(x)}

#make cdfs for mixture predictions
pmdist1 <- function(x) {distr::p(mdist1)(x)}
pmdist2 <- function(x) {distr::p(mdist2)(x)}

#realized observation
ob <- 3

#posterior model probability for calculating weights
w1 <- pmdist1(ob)/(pmdist1(ob) + pmdist2(ob))
w2 <- 1-w1
#w1 => 0.5286434
#w1 => 0.4713566

#build ensemble with calculated weights
ensdist <- distr::UnivarMixingDistribution(mdist1,
                                           mdist2,
                                           mixCoeff = c(w1,w2))

#pdf and cdf for ensemble
densdist <- function(x) {(distr::d(ensdist)(x))}
pensdist <- function(x) {(distr::p(ensdist)(x))}

#LogS for predictions at the realized observation
-log(dmdist1(ob)) # => 1.547238
-log(dmdist2(ob)) # => 1.848796
-log(densdist(ob)) # => 1.678156

#CRPS for predictions at the realized observation
CRPS(pmdist1,y=ob) # => 0.6348212
CRPS(pmdist2,y=ob) # => 0.5306083
CRPS(pensdist,y=ob) # => 0.5486368
\end{lstlisting}

Figure \ref{figmixs} below shows the density plots for each of the two mixture
distribution forecasts and the ensemble from the toy example.

\begin{figure}[htbp]
\centerline{\includegraphics[scale=.15]{mix_dists.png}}
\caption{Figure this out later}
\label{figmixs}
\end{figure}

\section{Discussion}

In this paper we have reviewed four representation types commonly used in
probabilistic 
forecasting including proper scoring, data storage and ensemble model 
construction for each type. We presented the discrete mixture distribution
representation and argue that in terms of model flexibility, storage and 
ensemble building it is
comparable to discretized bins and interval forecasts but also provides a 
forecast with a continuous nominal resolution. Thus we advocate its use in
future forecasting projects like those done by the CDC and COVID-19 Forecast 
Hub.

% Variables of R dataframe to b used in making mixture distribution 
% \begin{center}
%     \begin{tabular}{ | l | p{4cm} | p{7cm} |}
%     \hline
%     Argument & Summary & Options \\ \hline
%     dist & A string specifying a distribution family.  & “Beta”, “Cauchy”, 
%     “Lnorm”, “Logis”, “Unif”, “Lst” (location scale t distribution), 
%     “Weibull”, “Fd”, “Norm”,  “Chisq”, 
%     “Gammad”, “Exp”
% 	 “Binom”, “Dirac”, “Pois”, “Hyper”, “Nbinom”, “Geom” \\ \hline
%     param1 & A real number specifying the first parameter value of the 
%     distribution. & Beta: shape1; 
% 	Cauchy: location; 
% 	Lnorm: meanlog; 
% 	Logis: location; 
% 	Unif: min; 
% 	Lst: location; 
% 	Weibull: shape;
% 	Fd: df1;
% 	Norm: mean;
% 	Chisq: df;
% 	Gammad: scale;
% 	Exp: rate; 
% 	Binom: size;
% 	Dirac: location;
% 	Pois: lambda;
% 	Hyper: m;
% 	Nbinom: n;
% 	Geom: prob
%      \\ \hline
%     param2 & A real number specifying the second parameter value of the 
%     distribution. & Beta: shape2; 
% 	Cauchy: scale; 
% 	Lnorm: slog; 
% 	Logis: scale; 
% 	Unif: Max; 
% 	Lst: scale; 
% 	Weibull: scale; 
% 	Fd: df2; 
% 	Norm: sd; 
% 	Chisq: ncp; 
% 	Gammad: shape; 
% 	Binom: prob; 
% 	Hyper: n; 
% 	Nbinom: p \\
%     \hline
%     param3 & A real number specifying the third parameter value of the 
%     distribution. & Lst: df;
% 	Hyper: k \\
% 	\hline
% 	weight & A real number between 0 and 1 specifying the weight given to the 
% 	distribution in the overall mixture distribution. The sum of the weight 
% 	column should equal 1. & ...
% 	\\
% 	\hline
%     \end{tabular}
% \end{center}

% \newpage
% % \begin{adjustwidth}{-3cm}{-1cm}
% \begin{center}
% % \caption{MakeDist parameter options}
%     \begin{tabular}{ l l  p{2cm}  p{2cm}  p{2cm}}
%     \hline
%     \textbf{Distribution} & \textbf{dist} & \textbf{param1} & \textbf{param2} & 
%     \textbf{param3} \newline \\ \hline
%     Beta & Beta & shape1 & shape2 &  \\ 
%     Cauch & Cauchy & location & scale &  \\
%     Log-normal & Lnorm & meanlog & slog &  \\
%     Logistic & Logis & location & scale &  \\
%     Uniform & Unif & min & max &  \\
%     Location Scale T & Lst & location & scale & df \\
%     Weibull & Weibull & shape & scale &  \\
%     F & Fd & df1 & df2 &  \\
%     Normal & Norm & mean & sd &  \\
%     Chisqure & Chisq & df &  &  \\
%     Gamma & Gammad & scale & shape &  \\
%     Exponential & Exp & rate &  &  \\
%     Binomial & Binom & size & prob &  \\
%     Dirac & Dirac & location &  &  \\
%     Poisson & Pois & lambda &  &  \\
%     Hypergeometric & Hyper & m & n & k \\
%     Negative binomial & Nbinom & n & p &  \\
%     Geometric & Geom & prob &  &  \\ \hline
%     \end{tabular}
% \end{center}
% % \end{adjustwidth}
